Machine Learning guided workflow for Ribosome Binding Site engineering

### 2021-05-18 paper/main.tex
update plots

\begin{figure}[!ht]
    \centering
    \includegraphics[scale=0.4]{plots/Main_Paper/swarmplot.pdf}
    \includegraphics[scale=0.4]{plots/Main_Paper/quantplot.pdf}
    \includegraphics[scale=0.4]{plots/Main_Paper/histogram.pdf}
    \includegraphics[scale=0.4]{plots/Main_Paper/tsneplot.pdf}
    \caption{\cheng{May need to use subfigure to label the figures as A,B,C,D. I recall a discussion that C colours with viridis makes it hard to see the different histograms. But let's keep to the viridis colours. Also, if it is not too hard, make the bin edges [0, 0.1, 0.2, ...].}
    \textbf{TIRs of RBS groups examined in this study.} 
    The TIR results in all subplots are shown normalised to the respective benchmark sequence sample which acts as internal standard, that is TIR of a given RBS is divided by TIR of the benchmark RBS run in the same plate. 
    \textbf{A)} Swarm plot showing the obtained TIRs divided into RBS groups.
    BPS-NC: base-by-base changes in the non-core region. 
    BPS-C: base-by-base changes in the core region. 
    UNI: Randomly generated sequences with uniform distribution. 
    PPM: Randomly generated sequences with distribution following the PPM for all natural RBS in \emph{E. coli}. 
    Bandit-0/1/2/3 - Bandit algorithm generated results for Round 0, 1, 2 and 3 respectively.
    SD - Shine-Dalgarno sequence.
    Dash line is set to 1 and represents the averaged benchmark sequence TIR for that group. 
    BN - benchmark sequences for all plates. 
    They are not all exactly 1 due to them being shown as separate samples rather than averages.
    \maciej{Can we add a "BN" letters similar to the SD near the red group?.}
    \textbf{B)} Line plot showing TIR obtained in a given quantile of results divided into groups as in A).
    % save the random groups which were shown together due to similar distributions.
    UNI and PPM are merged into Random group and BPS-NC was removed due to changes being made outside the core in this group. 
        \textbf{C)} Histogram with kernel density estimations (KDE) showing distributions of TIRs for Bandit groups.
    \textbf{D)} tSNE plot showing the relative distances between sequences in our design spaces as calculated by our kernel function (weighted degree kernel with shift). The size \cheng{(area or diameter?, should be area)} of the circle represents the experimentally obtained TIR for measured groups.}
    \label{fig: Swarmplot and Quantplot}
\end{figure}

>>>>

\begin{figure}[!ht]
    \centering
    \includegraphics[scale=0.4]{plots/Main_Paper/swarmplot.pdf}
    \includegraphics[scale=0.4]{plots/Main_Paper/quantplot.pdf}
    \includegraphics[scale=0.4]{plots/Main_Paper/histogram.pdf}
    \includegraphics[scale=0.4]{plots/Main_Paper/tsneplot.pdf}
    \caption{\cheng{May need to use subfigure to label the figures as A,B,C,D.}
    \textbf{TIRs of RBS groups examined in this study.} 
    The TIR results in all subplots are shown normalised to the respective benchmark sequence sample which acts as internal standard, that is TIR of a given RBS is divided by TIR of the benchmark RBS run in the same plate. 
    \textbf{A)} Swarm plot showing the obtained TIRs divided into RBS groups.
    BPS-NC: base-by-base changes in the non-core region. 
    BPS-C: base-by-base changes in the core region. 
    UNI: Randomly generated sequences with uniform distribution. 
    PPM: Randomly generated sequences with distribution following the PPM for all natural RBS in \emph{E. coli}. 
    Bandit-0/1/2/3 - Bandit algorithm generated results for Round 0, 1, 2 and 3 respectively.
    SD - Shine-Dalgarno sequence.
    Dash line is set to 1 and represents the averaged benchmark sequence TIR for that group. 
    BN - benchmark sequences for all plates. 
    They are not all exactly 1 due to them being shown as separate samples rather than averages.
    \textbf{B)} Line plot showing TIR obtained in a given quantile of results divided into groups as in A).
    % save the random groups which were shown together due to similar distributions.
    UNI and PPM are merged into Random group and BPS-NC was removed due to changes being made outside the core in this group. 
        \textbf{C)} Histogram with kernel density estimations (KDE) showing distributions of TIRs for Bandit groups.
    \textbf{D)} tSNE plot showing the relative distances between sequences in our design spaces as calculated by our kernel function (weighted degree kernel with shift). 
    The area size of the circle represents the experimentally obtained TIR for measured groups.}
    \label{fig: Swarmplot and Quantplot}
\end{figure}
